Tabsets

### 2024-07-09 app_par.qmd
tabsets

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/app_par.qmd')
quarto::quarto_preview(pre_fil)
params <- list(name="1")
#lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
```

```{r, echo=F}
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
library(ManifoldDestiny)
library(dplyr)
library(ggplot2)
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(combinat)
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md$tabsets
mda <- md['1']
app1_rp <- selreport(app1,md$app1)
app_a_out <- seloutput(app1_rp)
```

```{r, echo=F}
mda <- md['1']
app1_rp <- selreport(app1,md$app1)
app_a_out <- seloutput(app1_rp)
```

## Application: `r mda$nmn`

### Information
- Election system:
  - Type of race: `r mda$race$rcn` 
  - Candidates: `r mda$race$cnd` 
  - Modes of voting: `r mda$race$mod`

- $H_0:$ Normal election 
- $H_1:$ Rigged election: 
  - Manifold object `r mda$mtd$sgs$eq[1]`
  - Solved for `r mda$mtd$sgs$va`

[Link to raw data and independent calculcations](`r mda$sht$url`)

>>>>

```{r, echo=F,message=FALSE,warning=FALSE}
ManifoldDestiny::wasmconload()
#library(ManifoldDestinyWASMP)
#library(ManifoldDestinyWASMD)
#library(ManifoldDestiny)
#library(dplyr)
#library(ggplot2)
#library(dplyr)
#library(combinat)
#library(htmltools)
#library(ggplot2)
#library(broom)
#library(combinat)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
mda <- app0[[2]]
app0_rp <- selreport(app0)
app_0_out <- seloutput(app0_rp)
mda$rcn
```

## Application: `r mda$nmn`
### Information
- Election system:
  - Type of race: `r mda$rcn` 
  - Candidates: `r mda$cnd` 
  - Modes of voting: `r mda$mod` 
- $H_0:$ Normal election 
- $H_1:$ Rigged election: 
  - Manifold object $`r mda$eq[1]`$
  - Solved for `r mda$va`

[Link to raw data and independent calculcations](`r mda$url`)

### Information

### {{< var tabh.h1 >}}

### {{< var tabs.h1 >}}

```{r, echo=F}
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
```
### {{< var tabs.h4 >}}
```{r, echo=F}
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
```
:::

```{r}
knitr::knit_exit()
```

### 2024-07-09 tabsets.qmd
appapr
tabsets

---
title: "Tabsets"
format: 
  html:
    page-layout: article
#filters:
#  - webr
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
#    footer: <https://lotariohw26.github.io/ManifoldDestiny/>
#execute: 
#  cache: false
bibliography: man_bib.bib
---

>>>>

---
title: "Tabsets"
format: 
  html:
    page-layout: article
#filters:
#  - webr
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
#    footer: <https://lotariohw26.github.io/ManifoldDestiny/>
#execute: 
#  cache: false
# app_par.qmd
bibliography: man_bib.bib
---

```{r, echo=F, message=F, warning=F}
ManifoldDestiny::wasmconload()
md <- ManifoldDestiny::metd
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
```

```{r}
knitr::knit_exit()
```
